\documentclass{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[english]{proposal}

\addbibresource{sources.bib}

\begin{document}

\section*{Curriculum Vitae}

\subsection*{Personal Data}

\begin{tabular}{|>{\raggedright}p{0.31\textwidth}|p{0.62\textwidth}|}
\hline
Title & \\
\hline
First name & \\
\hline
Name & \\
\hline
Current position &  \\
\hline
Current institution(s)/site(s), country & \\
\hline
Identifiers/ORCID & \\
\hline
\end{tabular}

\subsection*{Qualifications and Career}

\begin{tabular}{|>{\raggedright}p{0.38\textwidth}|p{0.55\textwidth}|}
\hline
\textbf{Stages} & \textbf{Periods and Details} \\
\hline
School, country & \\ % Required only for the Walter Benjamin Programme
\hline
Degree programme & \\
\hline
Doctorate & \\
\hline
Stages of academic/professional career & \\ % Optional after doctorate
\hline
\end{tabular}

\subsection*{Supplementary Career Information}

\subsection*{Engagement in the Research System}

\subsection*{Supervision of Researchers in Early Career Phases}

\subsection*{Scientific Results}
\nocite{*}

\subsubsection*{Category A}
\printbibliography[category=reviewed, heading=none]
\addtocategory{reviewed}{}

\subsubsection*{Category B}
\printbibliography[category=nonreviewed, heading=none]
\addtocategory{nonreviewed}{}

\subsection*{Academic Distinctions}

\subsection*{Other Information}

\subsection*{Data protection and consent to the processing of optional data}

If you provide voluntary information (marked as optional) in this CV, your consent is required.
Please confirm your consent by checking the box below.

% Uncomment one of the following lines to consent / not consent to information processing.
% [{\Large\textbf{\texttimes}}]
[\hspace{1em}]
\textbf{I expressly consent to the processing of the voluntary (optional) information, including ``special categories of personal data''%
\footnote{Special categories of personal data are those``revealing racial or ethnic origin, political opinions, religious or philosophical beliefs, or trade union membership, and (\dots) genetic data, biometric data for the purpose of uniquely identifying a natural person, data concerning health or data concerning a natural person's sex life or sexual orientation'' (Article 9(1) GDPR).
} in connection with the DFG's review and decision-making process regarding my proposal.}
This also includes forwarding my data to the external reviewers, committee members and, where applicable, foreign partner organisations who are involved in the decision-making process.
To the extent that these recipients are located in a third country (outside the European Economic Area), I additionally consent to them being granted access to my data for the above-mentioned purposes, even though a level of data protection comparable to EU law may not be guaranteed.
For this reason, compliance with the data protection principles of EU law is not guaranteed in such cases.
In this respect, there may be a violation of my fundamental rights and freedoms and resulting damages.
This may make it more difficult for me to assert my rights under the General Data Protection Regulation (e.g.\ information, rectification, erasure, compensation) and, if necessary, to enforce these rights with the help of authorities or in court.

I may \textbf{\underline{revoke}} my consent in whole or in part at any time -- with effect for the future, freely and without giving reasons -- vis-à-vis the DFG (\href{mailto:postmaster@dfg.de}{postmaster@dfg.de}).
The lawfulness of the processing carried out up to that point remains unaffected.
Insofar as I transmit ``special categories of personal data'' relating to third parties, I confirm that the necessary legitimation under data protection law exists (e.g.\ based on consent).

I have taken note of the DFG's Data Protection Notice relating to research funding, which I can access at \href{https://www.dfg.de/privacy_policy}{www.dfg.de/privacy\_policy} and I will forward it to such persons whose data the DFG processes as a result of being mentioned in this CV.\@

\end{document}
